### 2021-03-31 2_revisions/V6_ITT_major_revision/0_coverletter/itt-emotion-coverletter.tex
Add new stuff V6 to revisions history

We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.

We appreciate the consideration by your journal, the extensive reviews and are grateful for the opportunity to revise this further. This was a minor revision, with a few additions to the reviewed literature.

As stated before, We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels. We discuss theories on the reason behind this in our revised paper. We also found that Chinese tourists in Japan are interested in shopping at all price ranges of hotels, while Western tourists are more inclined to shop when staying in middle to high-priced hotels.

We believe this was an appropriate response to the minor revision, and hope we continue to be in your consideration.

>>>>

We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach" for further review by Information Technology \& Tourism.

We appreciate the consideration by your journal. In this revision, we were asked to make the text more concise and to review the English grammar. We performed a full check to the manuscript to remove sections of text that weren't necessary, made the text more concise and organized a few paragraphs differently, as well as making a few paragraphs belong to a new section in our discussion to avoid going off topic. We also improved on the abstract to make it more concise and appealing.

We believe this was an appropriate response to the major revision, and hope we continue to be in your consideration.
